### 2019-06-03 README.Rmd
renders README
adds tests for clean

```R
install.packages("Rclean")
```

@@

```R
install.packages("devtools")
devtools::install_github("ProvTools/Rclean", ref = "dev")
```

@@

```R
library(Rclean)
```

@@

```
clean("./example/simple_script.R")
```

@@

```
clean("./example/simple_script.R", "tab.15")
```

@@

```
my.code <- clean("./example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

@@

```R
write.code(my.code)
```

@@

```R
options(prov.json = readLines("prov_micro.json"))
```

@@

```R
clean(rp = TRUE)

@@

```R
clean(x, rp = TRUE)

>>>>

```{r}
install.packages("Rclean")
```

@@

```{r}
install.packages("devtools")
devtools::install_github("ProvTools/Rclean", ref = "dev")
```

@@

```{r}
library(Rclean)
```

@@

```{r}
clean("./example/simple_script.R")
```

@@

```{r}
clean("./example/simple_script.R", "tab.15")
```

@@

```{r}
my.code <- clean("./example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

@@

```{r}
write.code(my.code)
```

@@

```{r}
options(prov.json = readLines("prov_micro.json"))
```

@@

```{r}
clean(rp = TRUE)

@@

```{r}
clean(x, rp = TRUE)
